# Webex

Use the following code to install [webex](https://github.com/psyteachr/webex) from CRAN:
```
install.packages("webex")
```

```{block, type = "warning"}
If you're using bookdown 0.22, you need to use webex version 0.9.2 or above to avoid an error when you use the `hide()` function.
```

The `webex` package is called in the setup chunk, so you don't need to call it on every page you want to use webex. 

```{block, type = "info"}
If you're using webex outside of this bookdown template, such as in an rmarkdown webpage, you will need to set the output type to `webex::webex_default` in the yaml header in order to import the css and javascript files. To create a file from the webex template in RStudio, click **`File -> New File... -> RMarkdown`** and in the dialog box that appears, select **`From Template`** and choose **`Web Exercises`**.
```

## Fill-In-The-Blanks (`fitb()`) {#fitb}

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument (e.g., `fitb("4")`).

- 2 + 2 is `r fitb("4")`

You can also create these questions dynamically, using variables from your R session (e.g., `x <- sample(2:8, 1); fitb(x)`).

```{r echo = FALSE}
x <- sample(2:8, 1)
```

- The square root of `r x^2` is: `r fitb(x)`

The blanks are case-sensitive; if you don't care about case, use the argument `ignore_case = TRUE` (e.g., `fitb("E", ignore_case = TRUE)`).

- What is the letter after D? `r fitb("E", ignore_case = TRUE)`

If you want to ignore differences in whitespace use, use the argument `ignore_ws = TRUE` and include spaces in your answer anywhere they could be acceptable (e.g., `fitb("library( tidyverse )")`).

- How do you load the tidyverse package? `r fitb(c("library( tidyverse )", "library( 'tidyverse' )", "library( \"tidyverse\" )"), ignore_ws = TRUE, width = "20")`

You can set more than one possible correct answer by setting the answers as a vector (e.g., `fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`).

- Type a vowel: `r fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`

You can use regular expressions to test answers against more complex rules (e.g., `fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)`),.

- Type any 3 letters: `r fitb("^[a-zA-Z]{3}$", width = 3, regex = TRUE)`


## Multiple Choice (`mcq()`) {#mcq}

Make a multiple choice question by setting the first argument to `mcq()` to a vector where the answer(s) are labeled `answer` (e.g., `mcq(c("0", "3.14", answer = "42", "100", "none of the above"))`)

- "Never gonna give you up, never gonna: `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"
- "I `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))` down in Africa"
- "There's nothing that a hundred men `r mcq(c("on Mars", answer = "or more", "named Marv"))` could ever do"

## True or False (`torf()`) {#torf}

You can make a quick true-of-false option using `torf()` (e.g., `torf(FALSE)`).

- You can permute values in a vector using `sample()`. `r torf(TRUE)`

## Hidden solutions and hints (`hide()` and `unhide()`) {#hide-unhide}

You can fence off a solution area that will be hidden behind a button using `hide()` before the solution and `unhide()` after, each as inline R code.  Pass the text you want to appear on the button to the `hide()` function.

If the solution is an RMarkdown code chunk, instead of using `hide()` and `unhide()`, simply set the `webex.hide` chunk option to TRUE, or set it to the string you wish to display on the button.

- Recreate the scatterplot below, using the built-in `cars` dataset.

```{r plot-cars, echo = FALSE, fig.cap="Recreate this scatterplot."}
with(cars, plot(speed, dist))
```

`r hide("I need a hint")`
`?plot`
`r unhide()`

`r hide("Click here to see the solution")`
```{r}
plot(cars$speed, cars$dist)
```
`r unhide()`